The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-12-01 article_final/main.tex

The per-cycle complexity is $\mathcal{O}(mn^2 + n^2d + nd^2)$, where $m \geq n$ are the dimensions of the target matrix and $d$ is the size of the retained subspace (typically $d \ll n$).

>>>>

The per-iteration complexity of TRLan is $\mathcal{O}(mn)$, where $m \geq n$ are the dimensions of the target matrix.
